### 2016-07-21 R/ITHIM.Rmd
Update to webpage and created Makefile

```{r parameters}
(parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             ))
```

>>>>

```{r paameters}
(parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             ))

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
(METmatrix <- METmatrix/METmatrix[3,2])
```
